rmd revealjs Latex test

### 2020-04-29 nontex/revealjsrmd/test_img.Rmd
realjs rmd include tex preamble, clean tex comments, includechild

# Rmd RevealJS and Decktape
<!--
decktape convert to PDF
cd "C:/Users/fan/Tex4Econ/nontex/revealjsrmd/"
decktape automatic test_img.html test_img.pdf
-->

>>>>

# Rmd RevealJS and Decktape
<!--
# decktape convert to PDF
cd "C:/Users/fan/Tex4Econ/nontex/revealjsrmd/"
decktape automatic test_img.html test_img.pdf
-->

### 2020-04-29 nontex/revealjsrmd/test_tex.Rmd
realjs rmd include tex preamble, clean tex comments, includechild

<!--
decktape convert to PDF
cd "C:/Users/fan/Tex4Econ/nontex/revealjsrmd/"
decktape automatic test_tex.html test_tex.pdf
-->

@@

## INclude Equations and Symbols Defined Elsewhere

```{r echo=TRUE, eval=FALSE}
{r child = 'test_tex_define.tex'}
```

```{r child = 'test_tex_define.tex'}
```

>>>>

<!--
decktape convert to PDF
cd "C:/Users/fan/Documents/Dropbox (UH-ECON)/repos/Tex4Econ/nontex/revealjsrmd/"
decktape automatic test_tex.html test_tex.pdf
-->

@@

## Include Equations and Symbols Defined Elsewhere

Reuse tex preamble from paper, load as child, and clean comments.

```{r echo=TRUE, eval=FALSE}
# This loads the tex preamble with predefined formula, reuseable symbols etc.
test_tex_define_out = knitr::knit_child('test_tex_define.tex')
# Delete all comment lines, which starts with percent, and end with carriage return
# This deletes all but the last line
test_tex_define_out = gsub("\\%.*?\\\n", "", test_tex_define_out)
# Delete last comment if on final line
test_tex_define_out = gsub("\\\n%.*","", test_tex_define_out)
```

```{r include=FALSE, eval=TRUE}
test_tex_define_out = knitr::knit_child('test_tex_define.tex')
test_tex_define_out = gsub("\\%.*?\\\n", "", test_tex_define_out)
test_tex_define_out = gsub("\\\n%.*","", test_tex_define_out)
```

`r paste(test_tex_define_out, collapse='\n')`
